`r paste(params$species)` biomass trends and figures

### 2019-10-08 analysis/VOCC/1-split-biomass-by-maturity.Rmd
renderable versions of Rmds

---
title: "Spatiotemporal models of species biomass split by maturity class"
author: "Philina English"
date: '2019-07-18'
output: html_document
params: 
    species: "Arrowtooth Flounder"

---

Choose one value for each parameter:

Species
```{r}
species <- params$species

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Petrale Sole"
# species <- "English Sole"
# species <- "Dover Sole" # maturity data error for WCHG
# species <- "Southern Rock Sole"
# species <- "Flathead Sole"

# species <- "Silvergray Rockfish"
# species <- "Quillback Rockfish" # summer-birthing
species <- "Yelloweye Rockfish" # summer-birthing, overfished, 
# species <- "Bocaccio" # winter-birthing, overfished
# species <- "Sharpchin Rockfish"
# species <- "Splitnose Rockfish"

# species <- "Rougheye/Blackspotted Rockfish Complex"
# species <- "Redbanded Rockfish"
# species <- "Greenstriped Rockfish"
# # species <- "Copper Rockfish" # small sample
# species <- "Darkblotched Rockfish"
# # species <- "Shortbelly Rockfish" # small sample

# species <- "Pacific Ocean Perch" # schooling
# species <- "Widow Rockfish" # schooling
# species <- "Yellowtail Rockfish" # schooling
# species <- "Canary Rockfish" # schooling, winter-birthing
species <- "Shortraker Rockfish"

# species <- "Longspine Thornyhead"
# species <- "Shortspine Thornyhead"

# species <- "Walleye Pollock"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Lingcod"
# species <- "Pacific Hake"

# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Longnose Skate"
# species <- "Big Skate"
# species <- "Spotted Ratfish"
# # species <- "Sandpaper Skate" # small sample
# # species <- "Brown Cat Shark" # small sample
```

Region 
```{r}
region <- "All synoptic surveys"
# region <- "Both odd year surveys"
# region <- "West Coast Vancouver Island"
# region <- "West Coast Haida Gwaii"
```

Run all subsequent code...
```{r global_options, include=FALSE}
# covs <- gsub("\\+", "-", covariates)
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

@@

knitr::opts_chunk$set(fig.width=11, fig.height=8.5, 
                      fig.path=paste0("figs/", spp, "/"),
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

```{r, message=FALSE, warning=FALSE}

#fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

#### Calculate maturity weighted biomass if not done before
```{r}
 rm(biomass)
 rm(maturity)
# try(biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds")))

>>>>

---
title: "Split `r paste(params$species)` biomass by maturity class"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Curlfin Sole"
    region: "All synoptic surveys"
    #region: "Both odd year surveys"
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=8.5, 
                      fig.path=paste0("figs/", spp, "/"),
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

```{r params}
species <- params$species
region <- params$region

spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

@@

@@

#### Calculate maturity weighted biomass if not done before
```{r}
rm(biomass)
rm(maturity)

#try(biomass <- readRDS(paste0("data/", spp, "/data-by-maturity-", spp, "-", ssid_string, ".rds")))

### 2019-10-08 analysis/VOCC/2-biomass-depth-only-model.Rmd
renderable versions of Rmds

---
title: "Spatiotemporal models of species biomass with time-varying depth and trawl footprint, and optional substrate variables"
author: "Philina English"
date: '2019-07-18'
output: html_document
params: 
    species: "Arrowtooth Flounder"

---

Choose one value for each parameter:

Species
```{r}

```

Region 
```{r}
region <- "All synoptic surveys"
# region <- "Both odd year surveys"
# region <- "West Coast Vancouver Island"
# region <- "West Coast Haida Gwaii"
```

Choose model details
```{r}
priors <- FALSE
# priors <- TRUE
covariates <- "+trawled+as.factor(ssid)"
covs <- "-trawled-ssid"

# covariates <- "+muddy+any_rock"
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+rocky"
# covariates <- "+mixed_scaled+rocky_scaled+muddy_scaled"

# covs <- gsub("\\+", "-", covariates)
# covs <- gsub("\\+", "-", "+muddy+any_rock")
# covs <- gsub("\\+", "-", "-variable-substrate")
# covs <- gsub("\\+", "-", "-all-substrates")
```

Run all subsequent code...
```{r global_options, include=FALSE}
# covs <- gsub("\\+", "-", covariates)
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

@@

knitr::opts_chunk$set(
  fig.width = 11, fig.height = 8.5,
  fig.path = paste0("figs/", spp, "/"),
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)

fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

  starttime1 <- Sys.time()
  adult_biomass <- sdmTMB::sdmTMB(data,
    adult_formula,
    time_varying = ~ 0 + depth_scaled + depth_scaled2, #+ trawled
    time = "year", spde = spde,
    family = tweedie(link = "log"),
    ar1_fields = TRUE,
    include_spatial = TRUE,
    enable_priors = priors,
    control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
    silent = FALSE
  )
  endtime1 <- Sys.time()
  time1 <- round(starttime1 - endtime1)

@@

  starttime2 <- Sys.time()
  imm_biomass <- sdmTMB::sdmTMB(data,
    imm_formula,
    time_varying = ~ 0 + depth_scaled + depth_scaled2, #+ trawled
    time = "year", spde = spde,
    family = tweedie(link = "log"),
    ar1_fields = FALSE,
    include_spatial = TRUE,
    enable_priors = priors,
    control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
    silent = FALSE
  )
  endtime2 <- Sys.time()
  time2 <- round(starttime2 - endtime2)

  saveRDS(imm_biomass,
    file = paste0(
      "data/", spp,
      "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
    )
  )
} else {
  starttime3 <- Sys.time()
  dens_formula <- as.formula(paste("density ~ 0 + as.factor(year)", covariates, ""))

  total_biomass <- sdmTMB::sdmTMB(data,
    dens_formula,
    time_varying = ~ 0 + depth_scaled + depth_scaled2, # + trawled
    time = "year", spde = spde,
    family = tweedie(link = "log"),
    ar1_fields = TRUE,
    include_spatial = TRUE,
    enable_priors = priors,
    control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
    silent = FALSE
  )
  endtime3 <- Sys.time()
  time3 <- round(starttime3 - endtime3)

@@

```{r}
# covs <- gsub("\\+", "-", covariates)
fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

if (length(unique(fish$maturity_code)) > 2) {
  nd_all <- readRDS(paste0("data/nd_all_synoptic.rds"))
  adult_biomass <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

@@

  adult_predictions <- predict(adult_biomass, newdata = nd)
  saveRDS(adult_predictions, file = paste0(
    "data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds"
  ))

  imm_biomass <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_predictions <- predict(imm_biomass, newdata = nd)
  saveRDS(imm_predictions, file = paste0(
    "data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds"
  ))
} else {
  rm(adult_predictions)
  rm(imm_predictions)

  if (!exists(predictions)) {
    nd_all <- readRDS(paste0("data/nd_all_synoptic.rds"))
    nd <- nd_all %>% filter(ssid %in% model_ssid)
    nd <- na.omit(nd)
    nd$year <- as.integer(nd$year)

    total_biomass <- readRDS(paste0(
      "data/", spp,
      "/model-total-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
    ))
    predictions <- predict(total_biomass, newdata = nd)
    saveRDS(predictions, file = paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-total-biomass-prior-", priors, ".rds"
    ))
  }
}
```

>>>>

---
title: "Spatiotemporal models of `r paste(params$species)` biomass with time-varying depth and trawl footprint"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Copper Rockfish"
    region: "All synoptic surveys"
    covariates: "+trawled+as.factor(ssid)" # additional fixed-effect covariates
    covs: "-trawled-ssid" # covariate string used to name model rds 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=8.5, 
                      #fig.path=paste0("figs/", spp, "/"),
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

```{r params}
species <- params$species
region <- params$region
covariates <- params$covariates
covs <- params$covs
priors <- FALSE

paste("region =", region)
paste("model covariates =", covariates)
paste("model label =", covs)
paste("priors =", priors)
```

```{r, message=FALSE, warning=FALSE}
spp <- gsub(" ", "-", gsub("\\/", "-", tolower(species)))

@@

@@

  adult_biomass <- sdmTMB::sdmTMB(data,
    adult_formula,
    time_varying = ~ 0 + depth_scaled + depth_scaled2, #+ trawled
    time = "year", spde = spde,
    family = tweedie(link = "log"),
    ar1_fields = TRUE,
    include_spatial = TRUE,
    enable_priors = priors,
    control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
    silent = FALSE
  )

@@

  imm_biomass <- sdmTMB::sdmTMB(data,
    imm_formula,
    time_varying = ~ 0 + depth_scaled + depth_scaled2, #+ trawled
    time = "year", spde = spde,
    family = tweedie(link = "log"),
    ar1_fields = FALSE,
    include_spatial = TRUE,
    enable_priors = priors,
    control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
    silent = FALSE
  )

  saveRDS(imm_biomass,
    file = paste0(
      "data/", spp,
      "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
    )
  )

} else {

  dens_formula <- as.formula(paste("density ~ 0 + as.factor(year)", covariates, ""))

  total_biomass <- sdmTMB::sdmTMB(data,
    dens_formula,
    time_varying = ~ 0 + depth_scaled + depth_scaled2, # + trawled
    time = "year", spde = spde,
    family = tweedie(link = "log"),
    ar1_fields = TRUE,
    include_spatial = TRUE,
    enable_priors = priors,
    control = sdmTMBcontrol(step.min = 0.01, step.max = 1),
    silent = FALSE
  )

@@

```{r}
#fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

if (any(names(data) == "adult_density")) {
#if (length(unique(fish$maturity_code)) > 2) {
  nd_all <- readRDS(paste0("data/nd_all_synoptic.rds"))
  adult_biomass <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))

@@

  adult_predictions <- predict(adult_biomass, newdata = nd)
  saveRDS(adult_predictions, file = paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds"))

  imm_biomass <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_predictions <- predict(imm_biomass, newdata = nd)
  saveRDS(imm_predictions, file = paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds"))

} else {
    nd_all <- readRDS(paste0("data/nd_all_synoptic.rds"))
    nd <- nd_all %>% filter(ssid %in% model_ssid)
    nd <- na.omit(nd)
    nd$year <- as.integer(nd$year)

    total_biomass <- readRDS(paste0("data/", spp,
      "/model-total-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))
    predictions <- predict(total_biomass, newdata = nd)
    saveRDS(predictions, file = paste0("data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-total-biomass-prior-", priors, ".rds"))
}
```

### 2019-10-08 analysis/VOCC/2-biomass-trends.Rmd
renderable versions of Rmds

---
title: "Biomass trends and figures"
author: "Philina English"
date: '2019-07-18'
output: html_document
---

This file calls models built by "1-biomass-models.Rmd" and stiches the predictions saved therein together.

# Choose params

Species
```{r}

```

Region 
```{r}
region <- "All synoptic surveys"

# region <- "Both odd year surveys"
# region <- "West Coast Vancouver Island"
# region <- "West Coast Haida Gwaii"
```

Choose model details
```{r}
update_spatial_model <- FALSE
priors <- FALSE
# priors <- TRUE
# covariates <- ""
# covariates <- "+trawled"
# covs <- gsub("\\+", "-", covariates)
covariates <- "+trawled+as.factor(ssid)"
covs <- gsub("\\+", "-", "+trawled+ssid")
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+muddy+any_rock"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
```

Run all subsequent code...
```{r global_options, include=FALSE}

@@

# folder to hold figs for this species
dir.create(file.path("figs", spp))
dir.create(file.path("data", spp))

knitr::opts_chunk$set(
  fig.width = 11, fig.height = 8.5,
  # fig.path=paste0("figs/", spp, "/"),
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)

fish <- readRDS(paste0("raw/bio-data-", spp, ""))

@@

Bind together predictions from different models
```{r}
rm(adult_predictions)
rm(imm_predictions)
rm(predictions)

@@

rm(pred1n3_all)
rm(pred4_all)
rm(pred16_all)
# if (isFALSE(update_spatial_model)) {
if (region != "All synoptic surveys") {
  try(adult_predictions <- readRDS(paste0(
    "data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds"
  )))
  try(imm_predictions <- readRDS(paste0(
    "data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds"
  )))

@@

    try(predictions <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-total-biomass-prior-", priors, ".rds"
    )))

    if (!exists("predictions")) {
      paste("Total biomass predictions for this survey are also not available.")
    }
  }
} else {
  try({
    adult_predictions <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds"
    ))
  })
  try({
    imm_predictions <- readRDS(paste0(
      "data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds"
    ))
  })

  if (!exists("adult_predictions")) {
    # OR bind together predictions from different models
    try({
      pred1n3 <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-1n3-mature-biomass-prior-", priors, ".rds"
      ))
    })
    try({
      pred4 <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-4-mature-biomass-prior-", priors, ".rds"
      ))
    })
    try({
      pred16 <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-16-mature-biomass-prior-", priors, ".rds"
      ))
    })

@@

    try({
      pred1n3_imm <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-1n3-imm-biomass-prior-", priors, ".rds"
      ))
    })
    try({
      pred4_imm <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-4-imm-biomass-prior-", priors, ".rds"
      ))
    })
    try({
      pred16_imm <- readRDS(paste0(
        "data/", spp,
        "/predictions-", spp, covs, "-16-imm-biomass-prior-", priors, ".rds"
      ))
    })

    if (!exists("pred1n3_imm")) pred1n3_imm <- NULL
    if (!exists("pred16_imm")) pred16_imm <- NULL
    if (!exists("pred4_imm")) pred4_imm <- NULL
    imm_predictions <- rbind(pred1n3_imm, pred4_imm, pred16_imm)

@@

      try({
        predictions <- readRDS(paste0(
          "data/", spp,
          "/predictions-", spp, covs, "-", ssid_string, "-total-biomass-prior-", priors, ".rds"
        ))
      })

      if (!exists("predictions")) {
        try({
          pred1n3_all <- readRDS(paste0(
            "data/", spp,
            "/predictions-", spp, covs, "-1n3-total-biomass-prior-", priors, ".rds"
          ))
        })
        try({
          pred4_all <- readRDS(paste0(
            "data/", spp,
            "/predictions-", spp, covs, "-4-total-biomass-prior-", priors, ".rds"
          ))
        })
        try({
          pred16_all <- readRDS(paste0(
            "data/", spp,
            "/predictions-", spp, covs, "-16-total-biomass-prior-", priors, ".rds"
          ))
        })
        try({
          predictions <- rbind(pred1n3_all, pred4_all, pred16_all)
        })

        if (!exists("predictions")) paste("Total biomass predictions are not available.")
      }
    }
  }
}
```

@@

# Plots and trends

```{r, error=TRUE}
if (exists("adult_predictions")) {
  p_adult_all <- plot_facet_map(adult_predictions, "est_exp",
    raster_limits = c(0, max_raster),
    legend_position = "none",
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
  print(p_adult_all)
} else {
  p_adult_all <- plot_facet_map(predictions, "total_bio",
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))

@@

```{r}
if (exists("adult_predictions")) {
  if (1 %in% model_ssid) {
    adult_predictions1 <- adult_predictions %>% filter(ssid == 1)
  } else {
    adult_predictions1 <- NULL
  }

@@

```{r }
if (exists("out_mature")) {
  trawl_footprint <- sf::st_read(dsn = "data/trawl-footprint", layer = "Trawl_footprint")
  proj.to <- "+proj=utm +zone=9 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
  trawl_footprint <- sf::st_transform(trawl_footprint, crs = proj.to)

@@

```{r, error=TRUE}
if (exists("out_mature")) {
  data <- out_mature
  biotrend_ad <- plot_vocc(data,
    fill_col = "units_per_decade",
    fill_label = "Mature \nbiomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    white_zero = TRUE,
    high_fill = "deepskyblue3", # "lightseagreen", # limegreen",
    low_fill = "red", # "deeppink3",# "steel blue 4",
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0(
    "", species, " ", min(unique(adult_predictions[["year"]])), "-", max(unique(adult_predictions[["year"]]))
  ))
  biotrend_ad
} else {
  biotrend_ad <- plot_vocc(out_total,
    fill_col = "units_per_decade",
    fill_label = "Biomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    white_zero = TRUE,
    high_fill = "deepskyblue3", # "greenyellow", # limegreen",
    low_fill = "red", # "steel blue 4",
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0(
    "", species, " ", min(unique(predictions[["year"]])), "-", max(unique(predictions[["year"]]))
  ))
  biotrend_ad
}
```

```{r, error=TRUE}
if (exists("imm_predictions")) {
  p_imm_all <- plot_facet_map(imm_predictions, "est_exp",
    transform_col = fourth_root_power,
    raster_limits = c(0, max_raster)
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " immature biomass \n "))

@@

Trend plots
```{r}
png(
  file = paste0("figs/", spp, "/trends-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 11,
  height = 8.5
)
gridExtra::grid.arrange(
  # p_adult, p_imm,
  biotrend_ad, biotrend_im,
  nrow = 1
)
dev.off()
```

Spatiotemporal biomass plots
```{r}
biomass_plots <- c(p_adult, p_imm)

@@

Plot medley
```{r}
png(
  file = paste0("figs/", spp, "/exploratory-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 9.5,
  height = 12.5
)

>>>>

---
title: "`r paste(params$species)` biomass trends and figures"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Lingcod"
    region: "All synoptic surveys"
    bind_predictions: FALSE
    covs: "-trawled-ssid" # covariate string used to name model rds 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=11, fig.height=8.5, 
                      #fig.path=paste0("figs/", spp, "/"),
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggplot2)
library(gfplot)
library(gfdata)
library(sdmTMB)
library(gfranges)
```

```{r params}
species <- params$species
region <- params$region
bind_predictions <- params$bind_predictions
covs <- params$covs
priors <- FALSE

paste("region =", region)
paste("ssids modelled separately =", bind_predictions)
paste("model label =", covs)
paste("priors =", priors)

@@

@@

Load model predictions
```{r results = "hide"}
rm(adult_predictions)
rm(imm_predictions)
rm(predictions)

@@

rm(pred1n3_all)
rm(pred4_all)
rm(pred16_all)

if (region != "All synoptic surveys") {
  try(adult_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds"
  )))
  try(imm_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds"
  )))

@@

    try(predictions <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-", ssid_string, "-total-biomass-prior-", priors, ".rds"
    )))

    if (!exists("predictions")) {
      paste("Total biomass predictions for this survey are also not available.")
    }
  }
} else {

  try({adult_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-mature-biomass-prior-", priors, ".rds"
    ))
  })
  try({imm_predictions <- readRDS(paste0("data/", spp,
    "/predictions-", spp, covs, "-", ssid_string, "-imm-biomass-prior-", priors, ".rds"
    ))
  })

  # OR bind together predictions from different models
  if (bind_predictions) {
    try({pred1n3 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3-mature-biomass-prior-", priors, ".rds"
      ))
    })
    try({pred4 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-4-mature-biomass-prior-", priors, ".rds"
      ))
    })
    try({pred16 <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-16-mature-biomass-prior-", priors, ".rds"
      ))
    })

@@

    try({pred1n3_imm <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-1n3-imm-biomass-prior-", priors, ".rds"
      ))
    })
    try({pred4_imm <- readRDS(paste0("data/", spp,
      "/predictions-", spp, covs, "-4-imm-biomass-prior-", priors, ".rds"))
    })
    try({pred16_imm <- readRDS(paste0("data/", spp,
        "/predictions-", spp, covs, "-16-imm-biomass-prior-", priors, ".rds"))
    })

    if (!exists("pred1n3_imm")) pred1n3_imm <- NULL
    if (!exists("pred16_imm")) pred16_imm <- NULL
    if (!exists("pred4_imm")) pred4_imm <- NULL
    imm_predictions <- rbind(pred1n3_imm, pred4_imm, pred16_imm)
  }
  }

@@

      try({predictions <- readRDS(paste0("data/", spp,
        "/predictions-", spp, covs, "-", ssid_string, "-total-biomass-prior-", priors, ".rds"))
      })

      if (!exists("predictions")) {
        try({pred1n3_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-1n3-total-biomass-prior-", priors, ".rds"))
        })
        try({pred4_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-4-total-biomass-prior-", priors, ".rds"))
        })
        try({pred16_all <- readRDS(paste0("data/", spp,
          "/predictions-", spp, covs, "-16-total-biomass-prior-", priors, ".rds"))
        })
        try({
          predictions <- rbind(pred1n3_all, pred4_all, pred16_all)
        })

        if (!exists("predictions")) paste("Total biomass predictions are not available.")
      }
    }
```

@@

## Mature (or total) biomass predictions
```{r, error=TRUE}
if (exists("adult_predictions")) {
  p_adult_all <- plot_facet_map(adult_predictions, "est_exp",
    raster_limits = c(0, max_raster),
    legend_position = "none",
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " mature biomass \n(max = ", max_adult, " kg/ha)"))
  print(p_adult_all)
} else {
  p_adult_all <- plot_facet_map(predictions, "total_bio",
    transform_col = fourth_root_power
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " total biomass \n(max = ", max_bio, " kg/ha)"))

@@

### Split by survey (SSID)
```{r}
if (exists("adult_predictions")) {
  if (1 %in% model_ssid) {
    adult_predictions1 <- adult_predictions %>% filter(ssid == 1)
  } else {
    adult_predictions1 <- NULL
  }

@@

### Recent biomass with trawl footprint
```{r }
if (exists("out_mature")) {
  trawl_footprint <- sf::st_read(dsn = "data/trawl-footprint", layer = "Trawl_footprint")
  proj.to <- "+proj=utm +zone=9 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
  trawl_footprint <- sf::st_transform(trawl_footprint, crs = proj.to)

@@

## Trends in biomass density
```{r, error=TRUE}
if (exists("out_mature")) {
  data <- out_mature
  biotrend_ad <- plot_vocc(data,
    fill_col = "units_per_decade",
    fill_label = "Mature \nbiomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    white_zero = TRUE,
    high_fill = "deepskyblue3", # "lightseagreen", # limegreen",
    low_fill = "red", # "deeppink3",# "steel blue 4",
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0(
    "", species, " ", min(unique(adult_predictions[["year"]])), "-", max(unique(adult_predictions[["year"]]))
  ))
  biotrend_ad
} else {
  biotrend_ad <- plot_vocc(out_total,
    fill_col = "units_per_decade",
    fill_label = "Biomass \ntrend \n(kg/ha/decade)",
    raster_alpha = 1,
    vec_aes = NULL,
    white_zero = TRUE,
    high_fill = "deepskyblue3", # "greenyellow", # limegreen",
    low_fill = "red", # "steel blue 4",
    transform_col = fourth_root_power,
    legend_position = c(0.2, 0.25)
  ) + ggtitle(paste0(
    "", species, " ", min(unique(predictions[["year"]])), "-", max(unique(predictions[["year"]]))
  ))
  biotrend_ad
}
```

# Immature biomass density
### if available
```{r, error=TRUE}
if (exists("imm_predictions")) {
  p_imm_all <- plot_facet_map(imm_predictions, "est_exp",
    transform_col = fourth_root_power,
    raster_limits = c(0, max_raster)
  ) +
    labs(fill = "kg/ha") +
    ggtitle(paste0("", species, " immature biomass \n "))

@@

Save trend plots
```{r results = "hide"}
png(
  file = paste0("figs/", spp, "/trends-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 11,
  height = 8.5
)
gridExtra::grid.arrange(
  # p_adult, p_imm,
  biotrend_ad, biotrend_im,
  nrow = 1
)
dev.off()
```

Save spatiotemporal biomass plots
```{r results = "hide"}
biomass_plots <- c(p_adult, p_imm)

@@

Save plot medley
```{r results = "hide"}
png(
  file = paste0("figs/", spp, "/exploratory-", spp, covs, "-", ssid_string, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 9.5,
  height = 12.5
)
